Boosted Regression Trees for Predictive Auto-Tuning

### 2011-12-14 paper/draft1.tex
m
Add bar plot

@@

\begin{figure*}[!ht]
\centering
\includegraphics[width=.9\linewidth]{illustrator/fig_main_R1.pdf}
\caption{
Computation speed for novel problem configurations using predictive
vs. empirical auto-tuning.
(a) As more problem configurations are used to train the regression model,
the performance of predictive auto-tuning approaches that of empirical auto-tuning
despite taking only 0.1 seconds instead of 2 minutes.
(b) and (c) For a wide range of devices, implementation speeds found by predictive auto-tuning correlate tightly with
implementation speeds found by empirical auto-tuning.
%The boosted regression trees used for predictive auto-tuning generalize correctly across the implementation space.
}
\label{fig:fig_gflop_scatter}
\end{figure*}

Figure~\ref{fig:allstars} shows the effectiveness of empirical auto-tuning is in this setting.
Taking the GTX 295 as an example,
and averaging across the range of problem configurations in our study,
we find that empirically auto-tuned implementations are on average about
50\% faster than the reference implementation.
The reference in turn, is about 50\% faster than implementations that were empirically auto-tuned for a [randomly chosen] different argument configuration.
This shows that it is genereally not enough to auto-tune for particular argument configurations;
instead it is important to choose the right kernel for the job for each unique argument configuration (input-dependent auto-tuning).
\begin{figure}
\centering
\includegraphics[scale=.42]{allstars_mixup_295.pdf}
% XXX: NPTODO: ERROR BARS
% XXX: NPTODO: fix fonts for better proportions
\caption{Different arguments call for different kernels:
{\em left} is the average argument-specific empirical
auto-tuned performance across 100 random argument configurations,
{\em middle} is the average speed of our reference implementation,
{\em right} is the average speed of kernels auto-tuned for different argument configurations than the one being tested.
For 38/100 random confurations, the kernel auto-tuned for another problem could not even run on the GTX 295 hardware.
These points contributed a speed of 0, bringing down the average much lower than the reference.
Good performance across a variety of inputs requires {\em input-dependent auto-tuning}.
}
\label{fig:allstars}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=.42]{fig_ntrain_munctional0_580.pdf} % on vader
\caption{The effect of the invalid configuration score ($\zeta$) and training set
size on predictive auto-tuning.
Models trained on as few as 25 configurations outperformed the reference.
Models trained on 50 or more configurations rivaled empirical auto-tuning.
Moderate values of $\zeta$ between $\log(0.25)$ and $\log(0.75)$ are best.
}
\label{fig:fig_ntrain}
\end{figure}

>>>>

% TODO: proof read for GFLOP vs. GFLOPS -> we want GFLOP

@@

\begin{figure*}[!t]
\centering
\includegraphics[width=.9\linewidth]{illustrator/fig_main_R1.pdf}
\caption{
Computation speed for novel problem configurations using predictive
vs. empirical auto-tuning.
(a) As more problem configurations are used to train the regression model,
the performance of predictive auto-tuning approaches that of empirical auto-tuning
despite taking only 0.1 seconds instead of 2 minutes.
(b) and (c) For a wide range of devices, implementation speeds found by predictive auto-tuning correlate tightly with
implementation speeds found by empirical auto-tuning.
%The boosted regression trees used for predictive auto-tuning generalize correctly across the implementation space.
}
\label{fig:fig_gflop_scatter}
\end{figure*}

Figure~\ref{fig:allstars} shows the effectiveness of empirical auto-tuning is
in this setting.  Taking the GTX 295 as an example, and averaging across the
range of problem configurations in our study, we find that empirically
auto-tuned implementations are on average about 50\% faster than the reference
implementation.  The reference in turn, is about 50\% faster than
implementations that were empirically auto-tuned for a \emph{randomly chosen}
different argument configuration.  This shows that it is genereally not enough
to auto-tune for particular argument configurations; instead it is important to
choose the right kernel for the job for each unique argument configuration
(input-dependent auto-tuning).

@@

\begin{figure}[!t]
\centering
\includegraphics[width=\linewidth]{illustrator/fig_allstars_mixup_580_R1.pdf}
\caption{Different arguments call for different kernels:
{\em left} is the average argument-specific empirical
auto-tuned performance across 100 random argument configurations,
{\em middle} is the average speed of our reference implementation,
{\em right} is the average speed of kernels auto-tuned for different argument
configurations than the one being tested.  For 38/100 random confurations, the
kernel auto-tuned for another problem could not even run on the GTX 295
hardware.  These points contributed a speed of 0, bringing down the average
much lower than the reference.  Good performance across a variety of inputs
requires {\em input-dependent auto-tuning}.
}
\label{fig:allstars}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[scale=.42]{fig_ntrain_munctional0_580.pdf} % on vader
\caption{The effect of the invalid configuration score ($\zeta$) and training set
size on predictive auto-tuning.
Models trained on as few as 25 configurations outperformed the reference.
Models trained on 50 or more configurations rivaled empirical auto-tuning.
Moderate values of $\zeta$ between $\log(0.25)$ and $\log(0.75)$ are best.
}
\label{fig:fig_ntrain}
\end{figure}
